\textbf{Computational Fuzzy Extractors}

### 2013-05-14 trunk/CompFuzzExt.tex
Took care some notes.

\newcommand{\A}{\mathcal{A}}
\newcommand{\D}{\mathcal{D}}

@@

\begin{theorem}~\cite[Theorem 8]{venkatLecture}
\label{thm:random code good distance}
For prime $q, \delta\in [0, 1-1/q), 0<\epsilon< 1-H_q(\delta)$ and sufficiently large $m$, the following holds for $n = \lceil (1-H_q(\delta) - \epsilon)m\rceil$ .  If $\vA \in \Fq^{m\times n}$ is drawn uniformly at random, then the linear code with $\vA$ as a generator matrix has rate at least $(1-H_q(\delta) -\epsilon)$ and relative distance at least $\delta$ with probability at least $1-e^{-\Omega(m)}$.
\end{theorem}
Of particular, concern will be the case where $m = poly(n)\geq 2n$ and $\delta = O (\log n /n)$.  This setting of parameters satisfies \thref{thm:random code good distance}:
\begin{corollary}
\label{cor:code high distance}
Let $n$ be a parameter and let $m = \poly(n)\geq 2n$.  
Let $q$ be a prime and $t = O(\frac{m}{n}\log n )$.  For large enough values of $n$, when $\vA\in \Fq^{m\times n}$ is drawn uniformly, the code generated by $\vA$ has distance at least $t$ with probability at least $1-e^{-\Omega(m)}\geq 1-e^{-\Omega(n)}$.
\end{corollary}
\begin{proof}
Let $c$ be some constant.  Let $\delta = t/m = \frac{c\log n}{n}$.  We show the corollary for the case when $m = 2n$~(increasing the size of $m$ only increases the relative distance).  It suffices to show that for sufficiently large $n$, $1- H_q(\frac{c\log n}{n}) - \epsilon = 1/2$ or equivalently that $H_q(\frac{c\log n}{m})< 1/2$ as then setting $\epsilon = 1/2-H_q(\frac{c\log n}{n})$ satisfies  \thref{thm:random code good distance}.  For sufficiently large $n$:
\begin{itemize}
\item $\frac{c\log n}{n}< 1/2$, so we can work with the binary entropy function $H_2$.  
\item $\frac{c\log n}{n}< .1 < 1/2$ and thus $H_q(\frac{c\log n}{n})< H_q(.1)$. 
\end{itemize}  Putting these statements together, for large enough $n$, $H_q(\frac{c\log n}{n})< H_q(.1) < H_2(.1)< 1/2$ as desired.  This completes the proof.

@@

Let $\D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform where $\alpha$ of the equations have no error added.  That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha)}$, let $\vx$ be uniform over $\Fq^{(n+\alpha)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$. Furthermore, let $\vu$ be the uniform distribution over $\Fq^{m+\alpha}$.  We assume that, 
\[
|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
\]

@@

Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
Let $\D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.  That is, $\D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.  We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$. Let $\epsilon \geq 1/\poly(n)$, then, 
\[
|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
\]
We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.  Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.  It suffices to build a ppt distinguisher $\D'$  where 
\begin{align}
\label{eq:block LWE dist}
|\Pr[\D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[\D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
\end{align}
We will make a single call to $\D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.

\begin{figure}[t]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., m$:
\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., m$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $\D$ on input $\vA, \vb$.
\item Output $\D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
\label{cl:full rank matrix}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.  By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }=\ngl(n)\\
\end{align*}
Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
\end{proof}
\begin{corollary}
$
|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}

We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $\D'$ prepares a random instance in this case. We show this in the following three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve'$ and where $\ve_i' = \ve_i$ for $1\leq i\leq m$ and $\ve_i' = 0$ otherwise.
\item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
\end{enumerate}

@@

If $\D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.

@@

Finally, the reduction runs in polynomial time and together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $\D'$ properly prepares the instance thus, 
\begin{align*}
&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
&\, = \left| \Pr\left[\D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
&\, =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
\end{align*}
Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
\end{proof}
\section{Additional Proofs}

@@

\subsection{Proof of \lemref{lem:i t poly time}}
\label{sec:proof lem i t poly time}
\begin{proof}
Let $d$ be a constant and $t = d\log n\left( \frac{m}{n}-2\right)$.  
By \corref{cor:code high distance}, the code generated by $\vA$ has distance at least $t$ with probability $1-e^{-\Omega(n)}$.  Thus, a false matches occurs in step (5) with probability $e^{-\Omega(n)}$.  This probability is over the coins of $\gen$ and thus does not grow with the number of iterations in $\mathcal{I}_t$.  We consider the expected number of times step 2 is executed when $t\leq d\log n\left(\frac{m}{n}-1\right)$.  Steps (3-5) can be accomplished in time $n^3\log q $.  An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, \vc_{i_1,..., i_{2n}}$ have no error and when there is a sub matrix of $A_{i_1,..., i_{2n}}$ that has full rank.  The probability that $A_{i_1,..., i_{2n}}$ is full rank depends only on the coins of $\gen$ and is independent of the probability that $\vc_{i_1,...,i_{2n}}$ has no errors.  The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
\begin{align*}
\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n\left(\frac{m}{n}-2\right)}{m-i}\right)\\
&\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}
\end{align*}
Now, we consider the probability that no sub matrix of $\vA_{i_1,..., i_{2n}}$ has full rank.  This probability is at least $1-e^{-\Omega(n)}$~(see \clref{cl:full rank matrix}).  Thus, the probability that a given iteration succeeds $\frac{1}{n^{4d}} - e^{-\Omega(n)}$.  
Thus, the expected number of iterations in step 2 at most  $2n^{4d}$.  We assume all matrix operations can be completed in time $n^3\log q$, giving expected running approximately $O(n^{4d}(n^3 \log q))$.  
\end{proof}

@@

%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}$}
Note that $f$ is at most a constant in $n$.

Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
\begin{align*}
m &= \frac{(c+2d)n}{d}\\
q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
\end{align*}
Furthermore, we get decoding in time $O(n^{4d}(n^3\log n))$.  We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).  The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.  In \thref{thm:lossless secure conductor log}, we set $g=2$ and output the first half of $X$.  This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.  Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.

\subsection{Parameter Settings for \thref{thm:lossless block sketch log}}
\label{ssec:block params}
We repeat parameter settings for block fixing sources.  We now have $m+\alpha$ as the number of samples, while $n + \alpha+\omega(1)$ is the number of variables.  We can support any setting where $t, n, q, \rho, m, k, \alpha$ satisfy the following constraints~(for $\beta = \omega(1)$ and constants $d, f$):
\begin{align*}
n_0&< n -k  -\alpha -\beta\\
t&\leq d \log n\left(\frac{m}{n}-2\right)\\
q &= n^f\\
\rho q  &= 2n^{1/2+3\gamma}m\\
m\log \rho q &= k \log q
\end{align*}
Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
\begin{align*}
n_0&< n - k - \alpha -\beta\\
t&\leq d\log n\left(\frac{m}{n}-2\right)\\
m \log 2n^{1/2+3\gamma}m &= k \log n^f
\end{align*}
As before we can support any setting any $n, t, m, \alpha$ that satisfy these equations for $\beta = \omega(1)$ and constants $d, f$.  However, the last equation may have no solution for $f$ constant.  Putting the last equation in terms of $f$ one has:
\begin{align*}
n_0&< n -k  - \alpha - \omega(1) \\
t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
%f \log n &= \frac{m}{n}\log 2n^2m\\
f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
\end{align*}
To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k, \alpha = n/3$ and $\beta = \log n$.  Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
\begin{align*}
n_0&< n/3 -  \log n\\
m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}
\end{align*}

>>>>

\newcommand{\A}{\mathcal{A}}

@@

\begin{theorem}~\cite[Theorem 8]{venkatLecture}
\label{thm:random code good distance}
For prime $q, \delta\in [0, 1-1/q), 0<\epsilon< 1-H_q(\delta)$ and sufficiently large $m$, the following holds for $n = \lceil (1-H_q(\delta) - \epsilon)m\rceil$ .  If $\vA \in \Fq^{m\times n}$ is drawn uniformly at random, then the linear code with $\vA$ as a generator matrix has rate at least $(1-H_q(\delta) -\epsilon)$ and relative distance at least $\delta$ with probability at least $1-e^{-\Omega(m)}$.
\end{theorem}
Our setting is the case where $m = poly(n)\geq 2n$ and $\delta = O (\log n /n)$.  This setting of parameters satisfies \thref{thm:random code good distance}:
\begin{corollary}
\label{cor:code high distance}
Let $n$ be a parameter and let $m = \poly(n)\geq 2n$.  
Let $q$ be a prime and $t = O(\frac{m}{n}\log n )$.  For large enough values of $n$, when $\vA\in \Fq^{m\times n}$ is drawn uniformly, the code generated by $\vA$ has distance at least $t$ with probability at least $1-e^{-\Omega(m)}\geq 1-e^{-\Omega(n)}$.
\end{corollary}
\begin{proof}
Let $c$ be some constant.  Let $\delta = t/m = \frac{c\log n}{n}$.  We show the corollary for the case when $m = 2n$~(increasing the size of $m$ only increases the relative distance).  It suffices to show that for sufficiently large $n$, there exists $\epsilon>0$ where $1- H_q(\frac{c\log n}{n}) - \epsilon = 1/2$ or equivalently that $H_q(\frac{c\log n}{m})< 1/2$ as then setting $\epsilon = 1/2-H_q(\frac{c\log n}{n})$ satisfies  \thref{thm:random code good distance}.  For sufficiently large $n$:
\begin{itemize}
\item $\frac{c\log n}{n}< 1/2$, so we can work with the binary entropy function $H_2$.  
\item $\frac{c\log n}{n}< .1 < 1/2$ and thus $H_q(\frac{c\log n}{n})< H_q(.1)$. 
\end{itemize}  Putting these statements together, for large enough $n$, $H_q(\frac{c\log n}{n})< H_q(.1) < H_2(.1)< 1/2$ as desired.  This completes the proof.

@@

Let $D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform where $\alpha$ of the equations have no error added.  That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha)}$, let $\vx$ be uniform over $\Fq^{(n+\alpha)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$. Furthermore, let $\vu$ be the uniform distribution over $\Fq^{m+\alpha}$.  We assume that, 
\[
|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
\]

@@

Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.  That is, $D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.  We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$. Let $\epsilon \geq 1/\poly(n)$, then, 
\[
|\Pr[D(\vA, \vA\vx+\ve) = 1] - \Pr[D(\vA, \vu) =1]|> \epsilon.
\]
We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.  Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.  It suffices to build a distinguisher~(of polynomial size) $D'$  where 
\begin{align}
\label{eq:block LWE dist}
|\Pr[D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
\end{align}
We will make a single call to $D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $D'$ is given in \figref{fig:perfectLWEreduction}.

\begin{figure}[t]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., m$:
\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., m$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $D$ on input $\vA, \vb$.
\item Output $D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
\label{cl:full rank matrix}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.  By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }=\ngl(n)\\
\end{align*}
Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
\end{proof}
\begin{corollary}
$
|\Pr[D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}

We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $D'$ prepares a random instance in this case. We show this in the following three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve$ and where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
\item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
\end{enumerate}

@@

If $D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.

@@

Finally, the reduction runs in polynomial time and together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $D'$ properly prepares the instance thus, 
\begin{align*}
&\left|\Pr\left[D'(\vA', \vu') = 1\right]- \Pr\left[D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
&\, = \left| \Pr\left[D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
&\, =\left|\Pr\left[D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
\end{align*}
Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
\end{proof}
\section{Additional Proofs}

@@

\subsection{Proof of \lemref{lem:i t poly time}}
\label{sec:proof lem i t poly time}
\begin{proof}
Let $d$ be a constant and $t = d\log n\left( \frac{m}{n}-2\right)$.  
By \corref{cor:code high distance}, the code generated by $\vA$ has distance at least $t$ with probability $1-e^{-\Omega(n)}$.  Thus, a false matches occurs in step (5) with probability $e^{-\Omega(n)}$.  This probability is over the coins of $\gen$ and thus does not grow with the number of iterations in $\mathcal{I}_t$.  We consider the expected number of times step 2 is executed when $t\leq d\log n\left(\frac{m}{n}-1\right)$.  Steps (3-5) can be accomplished in time $n^3\log q $.  An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ have no error and when there is a sub matrix of $A_{i_1,..., i_{2n}}$ that has full rank.  The probability that $A_{i_1,..., i_{2n}}$ is full rank depends only on the coins of $\gen$ and is independent of the probability that $B_{i_1,...,i_{2n}}$ has no errors.  The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
\begin{align*}
\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n\left(\frac{m}{n}-2\right)}{m-i}\right)\\
&\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}
\end{align*}
Now, we consider the probability that some sub matrix of $\vA_{i_1,..., i_{2n}}$ has full rank.  This probability is at least $1-e^{-\Omega(n)}$~(see \clref{cl:full rank matrix}).  Thus, the probability that a given iteration succeeds $\frac{1}{n^{4d}} - e^{-\Omega(n)}$.  
Thus, the expected number of iterations in step 2 at most  $2n^{4d}$.  We assume all matrix operations can be completed in time $n^3\log q$, giving expected running approximately $O(n^{4d}(n^3 \log q))$.  
\end{proof}

@@

%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}$}
Note that $f$ is at a constant in $n$.

Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
\begin{align*}
m &= \frac{(c+2d)n}{d}\\
q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
\end{align*}
Furthermore, we get decoding in time $O(n^{4d}(n^3\log n))$.  We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).  The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.  In \thref{thm:lossless secure conductor log}, we set $g=2$ and output the first half of $X$.  This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.  %Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.

\subsection{Parameter Settings for \thref{thm:lossless block sketch log}}
\label{ssec:block params}
We repeat parameter settings for block fixing sources.  We now have $m+\alpha$ as the number of samples, while $n + \alpha+\omega(1)$ is the number of variables.  We can support any setting where $t, n, q, \rho, m, k, \alpha$ satisfy the following constraints~(for $\beta = \omega(1)$ and constants $d, f$):
\begin{align*}
n_0&< n -k  -\alpha -\beta\\
t&\leq d \log n\left(\frac{m}{n}-2\right)\\
q &= n^f\\
\rho q  &= 2n^{1/2+3\gamma}m\\
m\log \rho q &= k \log q
\end{align*}
Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
\begin{align*}
n_0&< n - k - \alpha -\beta\\
t&\leq d\log n\left(\frac{m}{n}-2\right)\\
m \log 2n^{1/2+3\gamma}m &= k \log n^f
\end{align*}
As before we can support any setting any $n, t, m, \alpha$ that satisfy these equations for $\beta = \omega(1)$ and constants $d, f$.  However, the last equation may have no solution for $f$ constant.  Putting the last equation in terms of $f$ one has:
\begin{align*}
n_0&< n -k  - \alpha - \beta \\
t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
%f \log n &= \frac{m}{n}\log 2n^2m\\
f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
\end{align*}
To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k, \alpha = n/3$ and $\beta = \log n$.  Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
\begin{align*}
n_0&< n/3 -  \log n\\
m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}
\end{align*}
